A Recurrent Network for Parallel Corpora Similarity Analysis

### 2018-07-26 WMT/divergence.tex
relecture complete - reste quelques doutes - look for FY

The remainder of this paper is structured as follows. 
Section~\ref{related} overviews related work. 
We describe in detail the core of the neural similarity classifier in Section~\ref{sec:similarity}. 
We report experiments with the presented model in Section~\ref{experiments}.
Section~\ref{sec:results} evaluates results. 
Finally, conclusions are drawn in Section~\ref{conclusions} and further work is outlined in Section~\ref{further}.
All the code used in this paper is freely available\footnote{https://github.com/anonymised}.

@@

Training is performed by minimising the loss in Equation~\eqref{loss_wemb}, for which examples with annotations for source $\mathcal{Y}_i^{src}$ and target $\mathcal{Y}_j^{tgt}$ words are needed.
Different kind of examples are used to train our network:
\begin{itemize}

@@

\item As negative examples, we use random unpaired sentences. In this case, all words are labelled as divergent, $\mathcal{Y}_i^{src}=+1$ and $\mathcal{Y}_j^{tgt}=+1$. 
Since negative examples may be very easy to classify and we want our network to detect less obvious divergencies, we further create negative examples following the next two methods:

\item We replace random sequences of words on either side of the sentence pair by a sequence of words with the same part-of-speeches. 
The rationale behind this method is to keep the new sentences as grammatical as possible. 
Otherwise, to predict divergence the network can learn to detect non-grammatical sentences.
Words that are not replaced are considered parallel ($-1$) while those replaced are assigned the divergent label ($+1$). 
Words aligned to some replaced words are also assigned the divergent label ($+1$). For instance, given the original sentence pair:

@@

In order to avoid that negative examples are easily predicted just by looking at the difference in length of training sentences we constraint all negative examples to have a difference in length not exceeding $2.0$. Very short sentences, of up to $4$ words, are accepted if the length ratio does not exceeds $3.0$.

\subsection{Fixing Translation Divergencies}
\label{correction}

We observed in our training corpora that many divergent sentences follow a common pattern, consisting of adding some extra leading/trailing words.
As in the first and second examples of table~\ref{tab:examples}.
Accordingly, we implemented a simple algorithm that discards sequences of leading/trailing words on both sides of the source and/or target sentences. 
Hence considering as parallel $s_u^v$ and $t_x^y$. 
To find the optimal source ($u, v$) and target ($x, y$) indices that enclose the parallel segments within the original sentence, we implement:
\begin{equation*}
\underset{u, v, x, y}{\arg\max} \Big \{      \underset{u \le I \le v}{\sum} \underset{x \le j \le y}{\max} \{ S(i,j) \}    \Big \}
\end{equation*}

The $\mathcal{N}$-best sequences following the previous function ($s_u^v$, $t_x^y$) are considered as valid corrections, but only the highest ranked according to its similarity score is used as replacement for the original $(s_1^I, t_1^J)$.
Short sentences are not considered. This is, $v - u > \tau$ and $y - x > \tau $. 
Figure~\ref{matrix} (left) shows an example of an alignment matrix $S(i,j)$ for a given sentence pair. 
An acceptable correction is: \textit{Que ressentez-vous ? $\Leftrightarrow$ What do you feel ?}. 
Hence, with indices $u=1$, $v=5$, $x=1$ and $y=3$.

@@

In this section we report on the experiments conducted to evaluate the proposed network. We begin with details of the corpora employed.

@@

Different corpora are used in this work to evaluate our similarity classifier.
We filter out divergencies found in the English-French OpenSubtitles corpus~\cite{LisonTiedemann2016}, which consists of a collection of movie and TV subtitles, aligned at the sentence level after a number of automatic preprocessing steps. 
The corpus presents many potential divergencies as outlined in Table~\ref{tab:examples}. 
To evaluate performance we used the En-Fr Microsoft Spoken Language Translation task, created from actual conversations over Skype~\cite{mslt-corpus-iwslt-2016-release}. 
%We also tested on a second domain, using the publicly available newstest-2013 En-Fr test set, corresponding to news stories selected from online sources~\cite{WMT:2013}.
In order to better assess the quality of our classifier when facing different types of word divergencies we collected from the original OpenSubtitles corpus and annotated at the word level $500$ sentences containing:
200 paired sentences;
100 unpaired sentences;
100 sentences with replace examples; and
100 sentences with insert examples as detailed in Section~\ref{training}.

We also use the Paracrawl corpus, which consists of a very noisy $1$ billion word (English token count) German-English corpus crawled from the web as part of the Paracrawl project\footnote{http://paracrawl.eu/}.
Performance is evaluated on the publicly available newstest-2017 En-De test set, corresponding to news stories selected from online sources~\cite{W17-4717}.

@@

After tokenisation, the $50,000$ most frequent words of each language are used as vocabulary.
Each out-of-vocabulary word is mapped to a special UNK token.
Our similarity classifier is described in Section~\ref{sec:similarity}. 
Word embeddings ($LT_s$ and $LT_t$) are initialised using \texttt{fastText}\footnote{https://github.com/facebookresearch/fastText}, further aligned by means of \texttt{MUSE}\footnote{https://github.com/facebookresearch/MUSE} following the unsupervised method detailed in~\cite{lample2018word}. 
Size of embeddings is $E_s=E_t=256$ cells. 
Both Bi-LSTM use 256-dimensional hidden representations ($E=512$). 
We use $r=1.0$. 
Optimization of the parameters is done using the stochastic gradient descent method along with gradient clipping (rescaling gradients whose norm exceeds a threshold) to avoid the exploding gradients problem~\cite{Pascanu:2013:DTR:3042817.3043083}. 
For each epoch we randomly select $1$ million sentence pairs that we place in batches of $32$ examples.  
Negative examples are created following the strategies detailed in~\ref{training}.
Word alignments and English part-of-speeches used to build negative examples were performed by \texttt{fast\_align}\footnote{https://github.com/clab/fast\_align} and \texttt{FreeLing}\footnote{https://github.com/TALP-UPC/FreeLing.git} respectively.
We run $10$ epochs and start decaying at each epoch by $0.8$ when score on validation set increases. 
Divergence is always computed following equation~\ref{cosine}. 
For divergence correction, we use $\mathcal{N}=20$ and $\tau=3$.

@@

In addition to the basic tokenisation detailed in Section~\ref{divergence} we perform Byte-Pair Encoding~\cite{Sennrich2016} with $30000$ merge operations learned joined from both language sides.
Neural MT systems are based on the open-source project  \texttt{OpenNMT}. 
We use a Transformer model with same configuration than in paper~\cite{vaswani2017attention}, i.e, both encoder and decoder have $6$ layers; Multi-head attention is performed over $8$ heads. 
Hidden layer's size is $512$. 
The inner layer of feed forward network is of size $2048$. 
Word embeddings have $512$ cells. We set the dropout probability to $0.1$. 
Batch size is set to $3072$.
%The maximum length of both source and target sentences is set to $80$ and we limit the vocabulary size to $50,000$ words for both source and target languages. 
The optimiser is Lazy Adam with $\beta_1 = 0.9$, $\beta_2 = 0.98$, $\epsilon = 10^{-9}$, $warmup\_steps = 4000$. We stop training after $30$ epochs.

@@

We evaluate first the ability of our similarity classifier to predict different types of divergencies at the level of words. 
We use the test set manually annotated for that purpose and train our model on the OpenSubtitles corpus.
In training, when different types of examples are used to train the network, the same number of examples are always considered for each type ({\texttt P}aired, {\texttt U}npaired, {\texttt R}eplace and {\texttt I}nsert). 
A word is considered divergent when associated to a negative aggregation score (see Equation~\ref{aggregation}).
Table~\ref{results_puri} shows accuracies obtained by our model when trained over different combinations of negative examples.% on the task of predicting wether words are divergent. 
We consider as divergent those words for which the similarity score predicted by our model, Equation~\ref{cosine}, is negative.

@@

As it can be seen, non-divergent words in parallel sentences (column \texttt{P}) are easy to identify. 
In all cases the accuracy reaches $100\%$. 
Divergent words in unpaired sentences (column \texttt{U}) are also easy to identify as far as the model has seen these types of examples in training. 
However, the accuracy drops dramatically when the model is not trained with unpaired sentences (rows  \texttt{PR}, \texttt{PI} and \texttt{PRI}).
Regarding columns \texttt{R} and \texttt{I}, accuracies are lower since these sentences contain a mix of divergent and non-divergent words. 
%Hence, word divergence is more difficult to predict. 
Again, models that were trained with the corresponding examples (\texttt{R} and \texttt{I}) obtain the highest accuracies (outlined in bold letters).
Column \texttt{PURI} shows accuracy results over the entire test set. This is, mixing all type of examples. 
As expected, the best accuracy is also obtained by the system trained on all type of  examples.

@@

\begin{figure}[h]
\centering
    \includegraphics[width=0.4\linewidth]{feel}    
    \includegraphics[width=0.4\linewidth]{feel_pu}    
\caption{Sentence pair with similarity scores produced by our model when trained over \texttt{PU} examples (right) and over \texttt{PURI} examples (left). Aggregation scores (Equation~\ref{aggregation}) are shown next to words. Matrices contain alignment scores. Sentence similarities (Equation~\ref{cosine})  shown below matrices.}
\label{matrix}
\end{figure}

Figure~\ref{matrix} illustrates the output of our network when trained using \texttt{PU} examples (right) and \texttt{PURI} examples (left).  
The former (right) fails to predict some word divergences, most likely because in training it never saw sentences mixing divergent and non-divergent words in the same example. 
Furthermore, the network trained over \texttt{PURI} examples (left) correctly assigns a lower similarity score to the sentence pair as both sentences do not convey the exact same meaning.

@@

Table~\ref{results_wemb} shows BLEU~\cite{P02-1040} scores of the same neural MT network when trained over different samples of the OpenSubtitles corpus.
Samples result from filtering sentences of the original corpus using different similarity thresholds.

@@

As it can be seen, the best performing training sample is obtained when using sentence pairs with similarity score in the range $[0.076, +\infty)$. 
This is, training with the most similar $18$ million sentences of the original data set. 
Note that despite assigned a positive similarity score, sentence pairs in the range $[0, 0.076]$ (almost $10$ million sentences) does not seem to contribute when training a neural MT network. 
On the contrary, when added as training data the MT accuracy is reduced.

Table~\ref{results} shows BLEU results for our neural MT engine trained over different data configurations:
The entire\footnote{The original Paracrawl corpus contains more than $100$ million sentences. We reduced its size to $22.2$ millions using standard filtering techniques.} data sets (\texttt{all}) of both corpora; 
Most similar pairs after as predicted by our network (\texttt{sim}); 
Finally, we apply the correction algorithm detailed in Section~\ref{correction} (\texttt{sim+fix}).
Columns Ref and Fix indicate the number of original and corrected sentences (in millions) considered to train the neural MT system.

@@

Regarding OpenSubtitles, when fixing $2.5$ million sentences ($4^{th}$ row) the accuracy is further boosted to $+2.01$, while the same sentence pairs does not show any improvement when added in their original form ($3^{rd}$ row).
%results are further improved $+2.01$ when fixing $2.5$ million sentences ($4^{th}$ row). 
%The same $2.5$ million sentences did not show any improvement when added in their original form

Similar results are obtained over the Paracrawl corpus. Results after fixing $2.5$ million sentences ($4^{th} row$) outperform those obtained by the same same sentence pairs when used by the neural MT system in their original form ($3^{rd} row$).

\section{Conclusions}
\label{conclusions}

We presented an unsupervised method based on deep neural networks for detecting translation divergences in parallel sentence pairs. 
The model also predicts misaligned words that can then be filtered out allowing for reusing some divergent sentences. 
We evaluated our model on two neural machine translation tasks, showing significant improvements when compared to training over the entire data set. 
%The method can be used on any parallel corpus without any manual annotation.

\section{Further Work}
\label{further}

%We plan to further evaluate divergence classification under different data noise levels. %and on additional language pairs. 
%as well as to measure the impact of using less noisy data when learning the similarity model
%We also would like to evaluate the impact of using less noisy (already filtered) data to learn the similarity model. 
%We would also like to use our model to predict other types of divergences 
We plan to use our model to predict sentence embeddings over monolingual corpora, allowing to collect parallel pairs through vector similarity measures.
%We also plan to further evaluate the correction algorithm.
In addition, we would like to measure the performance of our model after applying subword tokenisation,
%when working with a reduced vocabulary set, as a result of applying any subword tokenisation,
as well as using multiple LSTM layers, which is well known to capture hierarchical structure in the context of MT.

>>>>

The remainder of this paper is structured as follows. 
Section~\ref{related} overviews related work. 
We describe in detail the core of the neural similarity classifier in Section~\ref{sec:similarity}. 
We report experiments with the presented model in Section~\ref{experiments}.
Section~\ref{sec:results} evaluates results. 
Finally, we present some conclusions and discuss future work in
Section~\ref{conclusions+further}.
All the code used in this paper is freely
available\footnote{https://github.com/anonymised}.

@@

Training is performed by minimising the loss in
Equation~\eqref{loss_wemb}, for which annotated examples of
source $\mathcal{Y}_i^{src}$ and target $\mathcal{Y}_j^{tgt}$ words
are needed. 
Different kind of examples are used to train our network:
\begin{itemize}

@@

\item As negative examples, we use random unpaired sentences. In this
  case, all words are labelled as divergent, $\mathcal{Y}_i^{src}=+1$
  and $\mathcal{Y}_j^{tgt}=+1$.

Since negative examples may be very easy to classify and we want our
network to detect less obvious divergences, we further create negative
examples according to the next two methods:

\item We replace random sequences of words on either side of the sentence pair by a sequence of words with the same part-of-speeches. 
The rationale behind this method is to keep the new sentences as grammatical as possible. 
Otherwise, to predict divergence the network could learn to detect non-grammatical sentences.
Words that are not replaced are considered parallel ($-1$), whereas those replaced are assigned the divergent label ($+1$). 
Words aligned to some replaced words are also assigned the divergent label ($+1$). For instance, given the original sentence pair:

@@

In order to avoid that negative examples are easily predicted just by looking at the difference in length of training sentences we constraint all negative examples to have a difference in length not exceeding $2$. Very short sentences, of up to $4$ words, are accepted if the length ratio does not exceeds $3$.

\subsection{Fixing Translation Divergences}
\label{correction}

We observed in our training corpora that many divergent sentences follow a common pattern, consisting of adding some extra leading/trailing words.
This is for instance the case of the first and second examples in Table~\ref{tab:examples}.
Accordingly, we implemented a simple algorithm that discards sequences
of leading/trailing words on both sides of the source and/or target
sentences, and considers that only two substrings $s_u^v$ and $t_x^y$
of the original sentences are actually parallel.
To find the optimal source ($u, v$) and target ($x, y$) indices that
define the parallel segments in the original sentence, we solve:
\begin{equation*}
\underset{u, v, x, y}{\arg\max} \Big \{      \underset{u \le I \le v}{\sum} \underset{x \le j \le y}{\max} \{ S(i,j) \}    \Big \}.
\end{equation*}

The $\mathcal{N}$-best sequences following the previous function ($s_u^v$, $t_x^y$) are considered as valid corrections, but only the highest ranked according to its similarity score is used as replacement for the original $(s_1^I, t_1^J)$.
Short sentences are not considered. This is, we enforce $v - u > \tau$
and $y - x > \tau $, with $\tau$ a predefined parameter. 
Figure~\ref{matrix} (left) displays an example of an alignment matrix $S(i,j)$ for a given sentence pair. 
An acceptable correction is: \textit{Que ressentez-vous ?
  $\Leftrightarrow$ What do you feel ?}, corresponding to the 4-uples
of indices $u=1$, $v=5$, $x=1$ and $y=3$.

@@

In this section we report on the experiments conducted to evaluate our
architecture. We begin with details regarding our training and test corpora.

@@

Multiple corpora are used in this work to evaluate our similarity classifier.
We filter out divergencies found in the English-French OpenSubtitles corpus~\cite{LisonTiedemann2016}, which consists of a collection of movie and TV subtitles, aligned at the sentence level after a number of automatic preprocessing steps. 
The corpus presents many potential divergences as illustrated in Table~\ref{tab:examples}.

%We also tested on a second domain, using the publicly available newstest-2013 En-Fr test set, corresponding to news stories selected from online sources~\cite{WMT:2013}.
In order to better assess the quality of our classifier when facing different types of word divergences, we selected from the original OpenSubtitles corpus and annotated at the word level $500$ sentences containing:
200 paired sentences;
100 unpaired sentences;
100 sentences with replace examples; and
100 sentences with insert examples as detailed in Section~\ref{training}.

As an indirect evaluation of our filtering method, we also consider
two translation tasks.
Again using OpenSubtitles for training our system, we test on the En-Fr Microsoft Spoken Language Translation task, created from actual conversations over Skype~\cite{mslt-corpus-iwslt-2016-release}.

A second translation task uses the Paracrawl corpus, which consists of
a very noisy $1$ billion word (English token count) German-English
corpus crawled from the web as part of the Paracrawl
project\footnote{http://paracrawl.eu/}. Translation performance is evaluated on the publicly available newstest-2017 En-De test set, corresponding to news stories selected from online sources~\cite{W17-4717}.

@@

After tokenisation, the $50,000$ most frequent words of each language
define the vocabulary.
Each out-of-vocabulary word is mapped to a special UNK token.
% Our similarity classifier is described in Section~\ref{sec:similarity}. 
Word embeddings ($LT_s$ and $LT_t$) are initialised using \texttt{fastText}\footnote{https://github.com/facebookresearch/fastText}, further aligned by means of \texttt{MUSE}\footnote{https://github.com/facebookresearch/MUSE} following the unsupervised method detailed in~\cite{lample2018word}. 
The size of embeddings is $E_s=E_t=256$ cells. 
Both Bi-LSTMs use 256-dimensional hidden representations ($E=512$); and
we also set $r=1.0$ in Equation~\eqref{aggregation}.
Optimization of the parameters is done using stochastic gradient descent method along with gradient clipping (rescaling gradients whose norm exceeds a threshold) to avoid the exploding gradients problem~\cite{Pascanu:2013:DTR:3042817.3043083}. 
For each epoch, we randomly select $1$ million sentence pairs that we
place in batches of $32$ examples. We run $10$ epochs and start decaying at each epoch by $0.8$ when the
score on a validation set increases.

Negative examples are created following the strategies detailed in~\ref{training}.
Word alignments and English part-of-speeches used to build negative
examples were computed respectively by \texttt{fast\_align}\footnote{https://github.com/clab/fast\_align} and \texttt{FreeLing}\footnote{https://github.com/TALP-UPC/FreeLing.git}.
Divergence is always computed according to Equation~\eqref{cosine}. 
For divergence correction, we use $\mathcal{N}=20$ and $\tau=3$.

@@

In addition to the basic tokenisation detailed in Section~\ref{divergence}, we perform Byte-Pair Encoding~\cite{Sennrich2016} with $30000$ merge operations learned jointly from both language sides.
Neural MT systems are based on the open-source project  \texttt{OpenNMT}. 
We use a Transformer model with configuration similar to the
description in~\cite{vaswani2017attention}: both encoder and decoder
have $6$ layers; Multi-head attention is performed over $8$
heads. Additional parameters are set follows:
the hidden layer's size is $512$; the inner layer of the feed forward network is of size $2048$;
word embeddings have $512$ cells. We alsoe set the dropout probability
to $0.1$, and the batch size to $3072$.
%The maximum length of both source and target sentences is set to $80$ and we limit the vocabulary size to $50,000$ words for both source and target languages. 
The optimiser is Lazy Adam with $\beta_1 = 0.9$, $\beta_2 = 0.98$, $\epsilon = 10^{-9}$, $warmup\_steps = 4000$. We stop training after $30$ epochs.

@@

We first evaluate the ability of our similarity classifier to predict different types of divergences at the level of words. 
We use the manually annotated test set for that purpose and train our model on the OpenSubtitles corpus.
In training, when different types of examples are used to train the network, the same number of examples are always considered for each type ({\texttt P}aired, {\texttt U}npaired, {\texttt R}eplace and {\texttt I}nsert). 
A word is considered divergent when associated to a negative aggregation score (see Equation~\eqref{aggregation}).
Table~\ref{results_puri} reports the accuracies obtained by our model
when trained over different combinations of negative examples.% on the
                                % task of predicting wether words are
                                % divergent. 
% FY - Is it not contradictory with previous sentence ? Do you mean
% divergent *sentences*
We consider as divergent, words for which the similarity score predicted by our model, Equation~\eqref{cosine}, is negative.

@@

As it can be seen, non-divergent words in parallel sentences (column \texttt{P}) are easy to identify. 
In all cases the accuracy reaches $100\%$. 
Divergent words in unpaired sentences (column \texttt{U}) are also easy to identify as far as the model has seen these types of examples in training. 
However, the accuracy dramatically drops when the model is not trained with unpaired sentences (rows  \texttt{PR}, \texttt{PI} and \texttt{PRI}).
Regarding columns \texttt{R} and \texttt{I}, accuracies are lower since these sentences contain a mix of divergent and non-divergent words. 
%Hence, word divergence is more difficult to predict. 
Again, models that were trained with the corresponding examples (\texttt{R} and \texttt{I}) obtain the highest accuracies (outlined in bold letters).
Column \texttt{PURI} shows accuracy results over the entire test set,
that is, when mixing all type of examples. As expected, the best
accuracy is also obtained by the system trained on all type of  examples.

@@

\begin{figure}[h]
\centering
    \includegraphics[width=0.4\linewidth]{feel}    
    \includegraphics[width=0.4\linewidth]{feel_pu}    
\caption{Sentence pair with similarity scores produced by our model
  when trained over \texttt{PU} examples (right) and over
  \texttt{PURI} examples (left). Aggregation scores
  (Equation~\eqref{aggregation}) are shown next to words. Matrices
  contain alignment scores. Sentence similarities
  (Equation~\eqref{cosine})  are at the bottom.}
\label{matrix}
\end{figure}

Figure~\ref{matrix} illustrates the output of our network when trained using \texttt{PU} examples (right) and \texttt{PURI} examples (left).  
The former (right) fails to predict some word divergences, most likely because in training it never saw sentences mixing divergent and non-divergent words in the same example. 
Furthermore, the network trained over \texttt{PURI} examples (left) correctly assigns a low similarity score to the sentence pair, since both sentences do not convey the exact same meaning.

@@

Table~\ref{results_wemb} reports BLEU~\cite{P02-1040} scores of the same neural MT network when trained over different samples of the OpenSubtitles corpus.
Samples result from filtering sentences of the original corpus using different similarity thresholds.

@@

As it can be seen in Table~\ref{results_wemb}, the best performing
training sample is obtained when using sentence pairs with similarity
score in the range $[0.076, +\infty)$, which means training with the 
most similar $18$ million sentences in the original data set. 
Note that despite assigned a positive similarity score, sentence pairs in the range $[0, 0.076]$ (almost $10$ million sentences) does not seem to contribute when training a neural MT system. 
On the contrary, when they are added as training data, the MT accuracy is reduced.
% FY - cite standard filtering techniques
Table~\ref{results} reports BLEU results for our neural MT engine trained over three data configurations.
when using the entire\footnote{The original Paracrawl corpus contains more than $100$ million sentences. We reduced its size to $22.2$ millions using standard filtering techniques.} data sets (\texttt{all}) of both corpora; 
when using similar pairs after as predicted by our network (\texttt{sim}); 
after also applying the correction algorithm of Section~\ref{correction} (\texttt{sim+fix}).
Columns Ref and Fix indicate the number of original and corrected
sentences (in millions) used to train the neural MT system.

@@

Regarding OpenSubtitles, when fixing $2.5$ million sentences ($4^{th}$ row) the accuracy is further boosted to $+2.01$, while the same sentence pairs do not show any improvement when added in their original form ($3^{rd}$ row).
%results are further improved $+2.01$ when fixing $2.5$ million sentences ($4^{th}$ row). 
%The same $2.5$ million sentences did not show any improvement when added in their original form

Similar results are obtained with the Paracrawl corpus. Results after fixing $2.5$ million sentences ($4^{th} row$) outperform those obtained by the same same sentence pairs when used by the neural MT system in their original form ($3^{rd} row$).

\section{Conclusions and future work}
\label{conclusions+further}

We presented an unsupervised method based on deep neural networks for detecting translation divergences in parallel sentence pairs. 
The model also predicts misaligned words that can then be filtered
out, thus enabling us to reuse some divergent sentences. 
We evaluated our model on two neural machine translation tasks, 
reporting significant improvements when compared to training over the entire data set. 
%The method can be used on any parallel corpus without any manual annotation.

%We plan to further evaluate divergence classification under different data noise levels. %and on additional language pairs. 
%as well as to measure the impact of using less noisy data when learning the similarity model
%We also would like to evaluate the impact of using less noisy (already filtered) data to learn the similarity model. 
%We would also like to use our model to predict other types of
%divergences 
% FY - this should be on comparable corpora ?
We plan to use our model to predict sentence embeddings in monolingual corpora, allowing to collect parallel pairs through vector similarity measures.
%We also plan to further evaluate the correction algorithm.
In addition, we would like to measure the performance of our model after applying subword tokenisation,
%when working with a reduced vocabulary set, as a result of applying any subword tokenisation,
as well as using multiple LSTM layers, which is well known to capture hierarchical structure in the context of MT.
